NumPy---Array Programming in Python

### 2020-02-20 body.tex
Tiny textual fix ("their own")

These user-developers frequently had to write code from scratch to solve
their or their colleagues' problems---often in low-level languages
that precede Python, like Fortran \cite{dongarra2008netlib} and C.
To them, the advantages of an interactive, high-level array library
were evident. The design of this new tool was informed by other
powerful interactive programming languages for scientific computing
such as Basis \cite{dubois1989basis}, Yorick \cite{munro1995using}, R \cite{ihaka1996r},
and APL \cite{iverson1962programming},
as well as commercial languages and environments like IDL and {MATLAB}.

>>>>

These user-developers frequently had to write code from scratch to solve
their own or their colleagues' problems---often in low-level languages
that precede Python, like Fortran \cite{dongarra2008netlib} and C.
To them, the advantages of an interactive, high-level array library
were evident. The design of this new tool was informed by other
powerful interactive programming languages for scientific computing
such as Basis \cite{dubois1989basis}, Yorick \cite{munro1995using}, R \cite{ihaka1996r},
and APL \cite{iverson1962programming},
as well as commercial languages and environments like IDL and {MATLAB}.
